### 2024-08-14 data-visualization.qmd
20240813 - plot titles and highlighting

```{r}
library("tidyverse")
library("nflplotR")
library("plotly")
```

@@

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    color = "#000000",
    fill = "#0099F8"
  ) +
  theme_classic()
```

@@

```{r}
#| label: fig-density
#| fig-cap: "Density Plot of Fantasy Points."

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points,
    fill = position_group)
) +
  geom_density(alpha = 0.7) + # add transparency
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  geom_rug() +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasy_points,
    fill = position_group)
) +
  geom_boxplot() +
  theme_classic() + 
  theme(legend.position = "none")
```

@@

```{r}
#| label: fig-violin
#| fig-cap: "Violin Plot."

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasy_points,
    fill = position_group)
) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  theme_classic() + 
  theme(legend.position = "none")
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(player_display_name == "Tom Brady"),
  mapping = aes(
    x = season,
    y = fantasy_points,
    fill = position_group
    )
) +
  geom_line(
    linewidth = 1.5,
    color = "blue"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary,
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  geom_errorbar(
    aes(
      ymin = ci_lower,
      ymax = ci_upper),
    width = 0.2,
    color = "black"
  ) +
  theme_classic()
```

>>>>

```{r}
library("nflplotR")
library("plotly")
library("gghighlight")
library("tidyverse")
```

@@

A key principle of graphic design and data visualization is the importance of contrast.
Each visual component (e.g., line) that is important to see should be easy to distinguish.
For instance, you can highlight lines or points of interest to draw people's attention to the target of interest.
For examples of highlighting in figures, see Figures [-@fig-lineChartHighlighting] (@sec-lineChartHighlighting) and [-@fig-simulationOf10CoinFlips].

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    color = "#000000",
    fill = "#0099F8"
  ) +
  labs(
    x = "Fantasy Points",
    title = "Histogram of Fantasy Points"
  ) +
  theme_classic()
```

@@

```{r}
#| label: fig-density
#| fig-cap: "Density Plot of Fantasy Points by Position."

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points,
    fill = position_group)
) +
  geom_density(alpha = 0.7) + # add transparency
  labs(
    x = "Fantasy Points",
    fill = "Position",
    title = "Density Plot of Fantasy Points by Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  geom_rug() +
  labs(
    x = "Fantasy Points",
    title = "Histogram of Fantasy Points with Overlaid Density and Rug Plot"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasy_points,
    fill = position_group)
) +
  geom_boxplot() +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Box-and-Whisker Plot of Fantasy Points by Position"
  ) +
  theme_classic() + 
  theme(legend.position = "none")
```

@@

```{r}
#| label: fig-violin
#| fig-cap: "Violin Plot. Lines represent the 25th, 50th, and 75th quantiles."

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasy_points,
    fill = position_group)
) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Violin Plot by Position",
    subtitle = "Lines represent the 25th, 50th, and 75th quantiles"
  ) +
  theme_classic() + 
  theme(legend.position = "none")
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(player_display_name == "Tom Brady"),
  mapping = aes(
    x = season,
    y = fantasy_points
    )
) +
  geom_line(
    linewidth = 1.5,
    color = "blue"
  ) +
  labs(
    x = "Season",
    y = "Fantasy Points",
    title = "Bar Plot of Tom Brady's Fantasy Points by Season"
  ) +
  theme_classic()
```

### With Highlighting {#sec-lineChartHighlighting}

```{r}
#| label: fig-lineChartHighlighting
#| fig-cap: "Line Chart with Highlighting."

ggplot2::ggplot(
  data = player_stats_seasonal_offense,
  mapping = aes(
    x = season,
    y = fantasy_points,
    group = player_id,
    color = player_display_name)
) +
  geom_line() +
  gghighlight::gghighlight(
    player_display_name == "Tom Brady",
    label_key = player_display_name) +
  labs(
    x = "Season",
    y = "Fantasy Points",
    title = "Fantasy Points by Season and Player",
    subtitle = "(Tom Brady in Red)"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary,
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Bar Plot of Fantasy Points by Position"
  ) +
  theme_classic() + 
  theme(legend.position = "none")
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  geom_errorbar(
    aes(
      ymin = ci_lower,
      ymax = ci_upper),
    width = 0.2,
    color = "black"
  ) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Bar Plot of Fantasy Points by Position"
  ) +
  theme_classic() + 
  theme(legend.position = "none")
```
